The Effect of Events on Discussion in the Australian Federal Parliament (1901--2017)

### 2018-10-18 outputs/docs/events/paper.Rmd
Start discussion writeup

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    number_sections: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "The Effect of Events on Discussion in the Australian Federal Parliament (1901--2017)"
thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, Chris Cochrane and Dan Simpson for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources. Our dataset is available via an R package detailed at https://hansardr.com. Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We systematically analyse how parliamentary discussion changes in response to different types of events in Australian history. We first create a dataset of what was said in the Australian Federal Parliament from 1901 through to 2017 based on available public records. To reduce the dimensionality of this dataset we use a correlated topic model, and then analyse the effect of various events using a Bayesian hierarchical Dirichlet model. We find that: changes in government tend be associated with topic changes even when the party in power does not change; elections that do not result in a change in government are rarely associated with topic changes; economic events, such as financial crises, have less significant effects than other events such as terrorist attacks; and the effect of events is much more pronounced in the second half of our sample, and especially in the past two decades. Our findings have implications for how we think about the longer-term trajectory of government policymaking as the media and political cycles becomes increasingly focused on short-term events."
keywords: "text analysis, politics, Australia"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

Our work contributes to a growing modern quantitative social sciences literature that considers text as an input to more traditional methods, rather than requiring separate analysis. This literature sits across and draws from various historically-separate disciplines including economic history, political science, and applied statistics. We contribute to this literature in terms of both data and methods. To the best of our knowledge we are the first to bring to bear an essentially-complete record of what was said in the Australian Federal Parliament, and we make our dataset available to other researchers via an accompanying R package. From a methods perspective, our analysis model has several advantages over existing methods. These include: allowing the events to have more-complicated autocorrelated functional forms; implementing pooling across groups of similar documents; and identifying outlying topic distributions without the need to pre-specify the event of interest. As the digitisation of historical sources continues and computational power becomes cheaper, we expect interest in this approach to only increase.

@@

The Australian Federal Parliament makes daily Hansard records available online as PDFs and these are considered the official release. Additionally, XML records are available in some cases.[^XMLfootnote] We detail the sources of our Hansard PDFs in \@ref(hansardsources) and Appendix \@ref(examplehansardpage) provides an example of what a Hansard PDF looks like. There are 14,551 days worth of publicly available Hansard records across both chambers of the Australian Federal Parliament. Our data cleaning process indicates concerns with a small number of PDFs and these are detailed in Appendix \@ref(knownhansardissues).

@@

We use the Correlated Topic Model (CTM) [@BleiLafferty2007] to obtain estimated topic distributions over time. We consider these topic distributions as reduced dimension inputs that can be analysed within another model. We then formulate a Bayesian hierarchical Dirichlet model to assess changes in the topic distributions in relation to events of interest. In Appendix \@ref(word2vec), we include an alternative approach that follows @Taddy2015 by using word2vec, which more closely uses words, rather than topics, as an input.

@@

We run the model in JAGS using the \texttt{rjags} package of @Plummer2018. __An illustration of the validity of our analysis model using simulated data is in Appendix \@ref(modeldetailsandsimulation). __

@@

We summarise our results in terms of elections Table \@ref(tab:electionsresults) and in terms of governments in Table \@ref(tab:governmentsresults). Those tables focus on elections and governments that were different to the ones that preceeded them.

@@

<!-- 12;war, defence, country, ill, soldiers -->
<!-- 13;industry, trade, countries, development, country -->
<!-- 17;security, time, world, war, country -->
<!-- 22;war, country, matter, production, time -->
<!-- 23;defence, time, national, service, vietnam -->
<!-- 24;time, budget, tax, billion, million -->
<!-- 29;education, schools, students, school, university -->
<!-- 30;oil, energy, industry, nuclear, research -->
<!-- 32;industry, wheat, wool, growers, farmers -->
<!-- 33;per_cent, budget, time, tax, business -->
<!-- 35;community, time, health, support, local -->
<!-- 39;health, services, funding, care, million -->

@@

@@

We summarise the periods where parliamentary discussion was significantly different in Table X. **[Oh boy.]**

We summarise our results over time by looking at the standard deviation of sitting period estaimtes, around the mean election effect (Figure \@ref(fig:sigmaelection))

# Discussion
Groupings by government. This can be different to election groupings, for instance, the change from the Rudd to Gillard governments happened without an election. Similarly, John Howard's three terms are all considered the one government for our purposes.

@@

## Hansard sources {#hansardsources}

Hansard records are available from a variety of sources, as detailed in Table \ref{tab:hansardsourcestable}.

```{r hansardsourcestable, cache = TRUE, echo = FALSE, results = 'asis'}

hansard_sources %>%
  kable(
    booktabs = T,
    align = c('l', 'r', 'r', 'r'),
    caption = "Hansard sources and notes") %>%
  kable_styling(font_size = 10)

# Break cachee

Detail where from, and which years are being used and why.

Which years are being used (not non-OCRd)

@@

# word2vec alternative {#word2vec}
An alternative approach that follows @Taddy2015.

>>>>

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    number_sections: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "The Effect of Events on Discussion in the Australian Federal Parliament (1901--2017)"
thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, Chris Cochrane and Dan Simpson for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources. Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We systematically analyse how parliamentary discussion changes in response to different types of events in Australian history. We first create a dataset of what was said in the Australian Federal Parliament from 1901 through to 2017 based on available public records. To reduce the dimensionality of this dataset we use a correlated topic model, and then analyse the effect of various events using a Bayesian hierarchical Dirichlet model. We find that: changes in government tend be associated with topic changes even when the party in power does not change; elections that do not result in a change in government are rarely associated with topic changes; economic events, such as financial crises, have less significant effects than other events such as terrorist attacks; and the effect of events is much more pronounced in the second half of our sample, and especially in the past two decades. Our findings have implications for how we think about the longer-term trajectory of government policymaking as the media and political cycles becomes increasingly focused on short-term events."
keywords: "text analysis, politics, Australia"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

Our work contributes to a growing modern quantitative social sciences literature that considers text as an input to more traditional methods, rather than requiring separate analysis. This literature sits across and draws from various historically-separate disciplines including economic history, political science, and applied statistics. We contribute to this literature in terms of both data and methods. To the best of our knowledge we are the first to bring to bear an essentially-complete record of what was said in the Australian Federal Parliament, and we make our dataset available to other researchers via the R package \texttt{hansardr}. From a methods perspective, our analysis model has several advantages over existing methods. These include: allowing the events to have more-complicated autocorrelated functional forms; implementing pooling across groups of similar documents; and identifying outlying topic distributions without the need to pre-specify the event of interest. As the digitisation of historical sources continues and computational power becomes cheaper, we expect interest in this approach to only increase.

@@

The Australian Federal Parliament makes daily Hansard records available online as PDFs and these are considered the official release. Additionally, XML records are available in some cases.[^XMLfootnote] We provide an example of a Hansard PDF page in Appendix \@ref(examplehansardpage). There are 14,551 days worth of publicly available Hansard records across both chambers of the Australian Federal Parliament. Our data cleaning process indicates concerns with a small number of PDFs and these are detailed in Appendix \@ref(knownhansardissues).

@@

We use the Correlated Topic Model (CTM) [@BleiLafferty2007] to obtain estimated topic distributions over time. We consider these topic distributions as reduced dimension inputs that can be analysed within another model. We then formulate a Bayesian hierarchical Dirichlet model to assess changes in the topic distributions in relation to events of interest.

@@

We run the model in JAGS using the \texttt{rjags} package of @Plummer2018. __[An illustration of the validity of our analysis model using simulated data is in Appendix \@ref(modeldetailsandsimulation).] __

@@

We summarise our results in terms of elections Table \@ref(tab:electionsresults) and in terms of governments in Table \@ref(tab:governmentsresults). These tables focus on elections and governments that were different to the ones that preceeded them.

@@

@@

The topics that we have focused on here are:
12: war, defence, country, ill, soldiers; 
13: industry, trade, countries, development, country; 
17: security, time, world, war, country; 
22: war, country, matter, production, time; 
23: defence, time, national, service, vietnam; 
24: time, budget, tax, billion, million; 
29: education, schools, students, school, university; 
30: oil, energy, industry, nuclear, research; 
32: industry, wheat, wool, growers, farmers; 
33: per_cent, budget, time, tax, business; 
35: community, time, health, support, local; and
39: health, services, funding, care, million.

We summarise the periods where parliamentary discussion was significantly different in Table X. **[Oh boy. Not sure what to do here.]**

Finally, we summarise our results over time by looking at the standard deviation of sitting period estaimtes, around the mean election effect (Figure \@ref(fig:sigmaelection))

# Discussion

Of the 36 different governments, we find that 12 of them are significantly different to the government that preceeded them. However, two of these -- Page and the first Menezies government -- are likely due to the short length of the Page Government, and should be ignored, leaving only ten. The earliest of these is the second Menzies government starting in 1949, and these ten are concentrated in the second half of our sample, with three of them being in the past twenty years.

The significant difference of the second Menzies Government is associated with a variety of changes. The Chifley Government that preceeded it had finsih  For instance there was a large increase in the number of lower house seats at the 1949 election. This brought many new politicians into the house and it may be that they brought different topics.

Of the 45 general elections that have been held we find that 12 of them define periods that were significantly different to their immediate predecessor. 1974, 1980, 1990, 1998, 2004, and 2007 stand out as elections where the government did not change, but the model suggests there was considerable change in the topics discussed in parliament.

Groupings by government. This can be different to election groupings, for instance, the change from the Rudd to Gillard governments happened without an election. Similarly, John Howard's three terms are all considered the one government for our purposes.

@@

@@

@@
